Tablas_Ms_ HabitatAves

### 2020-12-18 Tablas_Ms_HabitatAves.Rmd
Arreglo tabla covariables

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(kableExtra)
library(tidyverse)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(kableExtra)
library(tidyverse)

```{r covariables, results='asis'}
DF_cov <- tibble( `Detection covariables`= c("Temperatura","Humedad", "DirViento" ,"RapViento", "Agua", " ", " ", " ", " ", " ", " ", " "), 
                   `Occupancy covariables`= c("Vegetation cover","Altitude","Distance to river",
                                              "Grassland", "Shrublands", "Native forest","Tree plantation" ,"Crops" ,
                                              "Paved surface","Sand", "Gravel", "Ocean" )
                   )

kable(DF_cov, booktabs=T, escape = F) %>% kable_styling(latex_options = "basic") %>% column_spec(column = 1, italic = T)
